\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-27 paper/cover_letter/cover_letter.tex
.

Please find our manuscript entitled "DTI-Voodoo: machine learning over interaction networks and
ontology-based background knowledge predicts drug--target
interactions" for your consideration. We therefore developed a novel method for drug--target interaction prediction (DTI) utilizing both ontology-encoded phenotypical and molecular features for both drugs and proteins. We further combine these methods with interaction networks, aiming for a more protein-centric prediction and evaluation.

We designed DTI-Voodoo under usage of graph convolutional neural network, exploiting the ``guilt-by-association`` principle and incorporate both top-down and bottom-up features into protein-protein interaction networks. Furthermore, we show that common DTI datasets share immanent biases, majorly influencing predictive DTI model performance evaluations. Thus, we propose a modified evaluation scheme, showing that DTI-Voodoo advances significantly over other state of the art DTI prediction approaches over several datasets.

The importance of DTI prediction for other challenges such as drug repurposing and repositioning makes DTI-Voodoo highly influential for a variety of researchers. Eventually, DTI-Voodoo's versatile methodology may be used over alternative protein-based representations to improve performances within other predictive tasks in the realm of bioinformatics and computational biology.

Therefore, we believe that
DTI-Voodoo will be well suited for the broad readership of
Bioinformatics.

>>>>

Please find our manuscript entitled "DTI-Voodoo: machine learning over
interaction networks and ontology-based background knowledge predicts
drug--target interactions" for your consideration.

DTI-Voodoo is a novel method for drug--target interaction (DTI)
prediction utilizing both ontology-based information about phenotypic
effects of drugs (side effects), and molecular features that encode
for interactions between drugs and proteins. We compare DTI-Voodoo to
seven state of the art DTI prediction methods on two datasets, and
significantly improve over all of them in our evaluation.

Moreover, we introduce several novel aspects to DTI prediction: First,
we identify, analyze, and correct for a number of inherent biases in
drug--target interaction prediction datasets; for this purpose, we
propose a ``naive'' classifier which does not make predictions based
on any biological information but achieves performance close to state
of the art methods.  Second, DTI-Voodoo combines indirect information
such as side effects and molecular properties of both drugs and
proteins in a novel way using an interaction network. Using this
network, we can demonstrate that side effect information ``localizes''
on the interaction network, i.e., that side effects are enriched on
modules consisting of interacting proteins, whereas molecular features
do not benefit from information the graph.

We believe that our results, as well as the novel methods we
introduced in developing DTI-Voodoo, makes our manuscript highly
suitable for the readers of Bioinformatics.
